Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-04-26 prevalence_testing/postshocktest2022draft.tex
minor edits; still need to finish argument

(\textcolor{red}{this needs work}) In Section \ref{sec:multhor} we discuss the background in \cite{quaedvlieg2021multi} that is necessary for our post-shock testing procedure. In Section \ref{modelsetup} we motivate time series models that we consider. In Section \ref{sec:aggmeth} we present aggregation strategies that we consider which inform our decision about the expected shock behavior.

@@

@@

The post-shock dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed. Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes. This makes distance based weighting an attractive avenue.

Next, we define the $h$-step forecast for $\mc{M}$, which plays an essential role in the framework of \citet{quaedvlieg2021multi}. Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^h$. Let the ordinary least squares (OLS) estimate for
\begin{align*}
	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}, \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
\end{align*}
 be 
 \begin{align*}
 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}, \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
 \end{align*}
Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^h$ is defined as
 \begin{align*}
 	\hat{y}_{i,t}^h &= \left(\hat{\eta}_i + \sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\tilde{\bs{\theta}}}_{i,j+1},
 \end{align*}
 where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$. This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature (\textcolor{red}{either provide a citation or remove this sentence}).

@@

\newpage
\textbf{Repeating for reference}:
\begin{align}
\mc{M} \colon \begin{array}{l}
  y_{i,t} = \eta_i + \left(\sum_{j=1}^{q_1}\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\theta_{i,j+1}'\mbf{x}_{i,t-j}\right)(1 - D_{i,t}) + f(\mathcal{F}_{i,t},\alpha_i)D_{i,t} + \varepsilon_{i,t},\\[.2cm]
  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]
  \; \alpha_i = \mu_{\alpha} + \delta_i'\mbf{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
  %\sum_{j=1}^{q_3}\delta_{i,j}'\mbf{x}_{i, T_i^*-j+1}+ \t{\varepsilon}_{i}, 
\end{array}\label{model-gen2}
\end{align}
where $D_{i,t} = I(t \geq T_i^* + 1)$, $I(\cdot)$ is the indicator function, $\x_{i,t} \in \R^{p}$ are fixed with $p \geq 1$. Let 
$\mathbf{\phi}_i = (\phi_{i,1},\ldots,\phi_{i,q_1})'$, 
$\mathbf{\theta}_i = (\theta_{i,1},\ldots,\theta_{i,q_2})'$, 
$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_{1}})'$, 
$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i, q_{2}})'$, 
$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,p})'$, 
and suppose that the regression coefficients in \eqref{model-gen2} have the following hierarchical random effects structure: 
\begin{equation} \label{random-effects2}
\begin{split}
  \eta_i &\simiid \mc{F}_{\eta} \text{ with }  \; \mrm{E}_{\mc{F}_{\eta}}(\eta_i) = \mu_\eta, \mrm{Var}_{\mc{F}_{\eta}}(\eta_i)  = \sigma^2_{\eta}, \\
  \mathbf{\phi}_{i,j} &\simiid \mc{F}_{\mathbf{\phi}_j} \text{ where } |\phi_{i,j}| < 1, \\
  \mathbf{\theta}_{i,j} &\simiid \mc{F}_{\mathbf{\theta}_j} \text{ with }  \; \mrm{E}_{\mc{F}_{\mathbf{\theta}_j}}(\theta_{i,j}) = \mu_{\mathbf{\theta}_j}, \mrm{Var}_{\mc{F}_{\mathbf{\theta}_j}}(\mathbf{\theta}_{i,j})  = \Sigma^2_{\mathbf{\theta}_j}, \\
  \mathbf{\delta}_i &\simiid  \mc{F}_{\mathbf{\delta}} \text{ with } \mrm{E}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\mu_{\mathbf{\delta}}, \mrm{Var}_{\mc{F}_{\mathbf{\delta}}}(\mathbf{\delta}_i)=\Sigma_{\mathbf{\delta}}, \\
\varepsilon_{i,t} & \simiid  \mc{F}_{\varepsilon_i} \text{ with }  \; \mrm{E}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t}) = 0, \mrm{Var}_{\mc{F}_{\varepsilon_i}}(\varepsilon_{i,t})  = \sigma^2_i,  \\
\varepsilon_{\alpha, i} &\simiid  \mc{F}_{\varepsilon_\alpha} \text{ with }\mrm{E}_{\mc{F}_{\varepsilon_\alpha}}(\varepsilon_{\alpha, i})=0, \mrm{Var}_{\mc{F}_{\varepsilon_{\alpha}}}(\varepsilon_{\alpha, i})=\sigma^2_{\alpha}, \\
  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}_j}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
  \tilde{\mathbf{\theta}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\theta}_j}}(\x_{i,T_i^*+1}),  \\  
 % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\
&\eta_i \indep \mathbf{\phi}_{i,j} \indep \mathbf{\theta}_{i,j} \indep 
\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 
\end{split}
\end{equation}

@@

We first present some intermediary technical results and definitions. Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$. Define  
\begin{align*}
  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right),
\end{align*}
and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$. Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ and some choice of $\varepsilon_1$. Pick some large $M > 0$. Fix $T = T_1 = T_{i'}$ and $T^* = T^*_1 = T^*_{i'}$. Define the events 
\begin{align*}
  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right. \\
  &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')\|_\infty < M\},  
\end{align*}
where $\tilde\varepsilon_t = \varepsilon_{1,t} - \varepsilon_{i',t} + D_{i,t}(\varepsilon_{\alpha,1} - \varepsilon_{\alpha,i'})$ and $\bm{\eta},\bm{\phi},\bm{\theta},\bm{\delta},\tilde{\bm{\phi}}$, and $\tilde{\bm{\theta}}$ are vectors containing the random effects in \eqref{random-effects} for indices $1$ and $i'$, and we take $\|\bm{a}\|_\infty = \max_j(|a_j|)$ . We will also suppose that $\|\x_{j,t}\|_\infty < M$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$. Note that both $\Prob(E_1^C) \to 0$ and $\Prob(E_2^C) \to 0$  as $\sigma^2 \to 0$ with $T$ and $n$ fixed. For simplicity we will set $q_1 = q_2 = 1$.

For all $t > T^*$ let $\tilde y_{i',t}$ possess the same dynamics as $y_{i',t}$ except that this process is shifted in a manner to reflect how $y_{i,t}$ changes for all $t > T^*$. More formally, we will let 
$$
  \tilde y_{i',t} = \left\{\begin{array}{cc}
  y_{i,t} & \text{when} \; t < T^*+1; \\ 
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}y_{1,t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t = T^* + 1; \\
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}\tilde y_{i',t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t > T^* + 1.
\end{array}\right.	
$$
The purpose of $\tilde y_{i',t}$ is to place the post-shock responses at the same starting point which allows us to avoid strong parametric specifications on the pre-shock dynamics. This series also contains terms which are estimable from the data. Define the event 
$$
  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M : t = 1,\ldots,T\}, 
$$
where $M$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$. We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$, 
\begin{align*}
	&|y_{1,t} - \tilde{y}_{i',t}| 
		= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1})
		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}) 
		+ (\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t}) + \tilde\varepsilon_t| \\
	&\qquad \leq |\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}|
		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}| 
		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
		+ \varepsilon_1 \\
	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
	&\qquad = \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
\end{align*}
With $T$ set, we can choose $\varepsilon_1$ small enough so that 
$
  |y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_2
$
for all $T^* < t \leq T $.

@@

We now bound the difference in loss differential vectors $\|\dbf_{1,t} - \dbf_{i',t}\|$ for $t > T^*$ when we specify the loss $L(a,b) = |a-b|$. The loss differential vector $\dbf_{1,t} \in \R^H$ has elements $|y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}|$. What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
$$
  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{i',h}_{1,t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{1,t}| + 2(\varepsilon_3 + \varepsilon_7).
$$
Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$.

@@

Recall from Section \ref{forecast}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively). We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence. The weighted voting procedure weight those testing indicators using $\mbf{W}^*$; and returns shock prevalence if the output exceeds 0.5 and shock transience if the output is smaller than 0.5. As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct. From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_0$ and $\mc{M}$ for different $L$. However, weighted voting suggests shock transience for $\mc{M}$ for different $L$ but shock prevalence for $\mc{M}_0$ and $L=15, 30$ and shock transience for $\mc{M}_0$ and $L = 7$. As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small. Note that Proposition \ref{votprop} and Corollary \ref{coro1} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$. Note that the interpretation and meaning of $p_1$ is closely connected with models. For example, $\mc{M}_0$ would imply a persistent shock whereas $\mc{M}$ is more general in suggesting changing dynamics. Thus, even if  this theoretical statement  may be correct, it makes practical sense only when model is identified well. This comment corresponds to the possibility that $\mc{M}_0$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}$.

>>>>

(\textcolor{red}{this needs work}) In Section \ref{modelsetup} we motivate time series models that we consider. In Section \ref{sec:multhor} we discuss the background in \cite{quaedvlieg2021multi} that is necessary for our post-shock testing procedure. In Section \ref{sec:aggmeth} we present aggregation strategies that we consider which inform our decision about the expected shock behavior.

@@

The post-shock dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed. Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|$ are expected to experience similar structural changes. This makes distance based weighting an attractive avenue.

Next, we define the $h$-step forecast for $\mc{M}$ which plays an essential role in the framework of \citet{quaedvlieg2021multi}. Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^{1,h}$. Let the ordinary least squares (OLS) estimate for
\begin{align*}
	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}', \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
\end{align*}
 be 
 \begin{align*}
 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}', \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}')' \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
 \end{align*}
Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^{1,h}$ is defined as
 \begin{align*}
 	\hat{y}_{i,t}^{1,h} &= \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{1,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{1,h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\tilde{\bs{\theta}}}_{i,j+1},
 \end{align*}
 where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$. This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature (\textcolor{red}{either provide a citation or remove this sentence}). The $h$-step forecast corresponding to the model that does include any post-shock changes $\hat{y}_{i,t}^{2,h}$ is defined similarly,
\begin{equation*}
 	\hat{y}_{i,t}^{2,h} = \hat{\eta}_i + \left(\sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{2,h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}'\hat{\bs{\theta}}_{i,j+1}\right).
\end{equation*}

@@

@@

\newpage

@@

We first present some intermediary technical results and definitions. Let $\lambda_{\text{max},\theta_k}$, $\lambda_{\text{max},\theta_\delta}$, $\lambda_{\text{max},\gamma}$ respectively be the largest eigenvalues of $\Sigma_{\theta_k}$, $\Sigma_{\delta}$, and $\Sigma_{\gamma}$ for $k = 1,\ldots,q_2$. Define  
\begin{align*}
  \mu_{\min} &= \min\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\min(\mu_\delta),\min(\mu_{\theta_k}),\min(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \mu_{\max} &= \max\left(\mu_\eta,\mu_{\phi_j},\mu_{\tilde\phi_j},\max(\mu_\delta),\max(\mu_{\theta_k}),\max(\mu_{\tilde\theta_k}); j = 1,\ldots,q_1, k = 1,\ldots,q_2\right), \\
  \lambda_{\max} &= \max\left(\lambda_{\text{max},\theta_k}, \lambda_{\text{max},\theta_\delta}, \lambda_{\text{max},\gamma}; k = 1,\ldots,q_2\right), \\
  \sigma^2_{\max} &= \max\left(\sigma^2_{\eta},\sigma^2_{\phi_j},\sigma^2_i,\sigma^2_{\alpha},\sigma^2_{\tilde{\phi}_j}; i = 1,\ldots,n+1, j = 1,\ldots,q_1\right),
\end{align*}
and let $\sigma^2 = \max(\lambda_{\max}, \sigma^2_{\max})$. Now fix $i'$ where we suppose that $\|\x_{1,t} - \x_{i',t}\| < \varepsilon_1$ for all $t$ and some choice of $\varepsilon_1$. Pick some large $M > 0$. Fix $T = T_1 = T_{i'}$ and $T^* = T^*_1 = T^*_{i'}$. Define the events 
\begin{align*}
  E_1 := &\left\{\max\left(|\|\delta_1 - \delta_{i'}\|,|\tilde\phi_{1,j}-\tilde\phi_{i',j}|,\|\tilde\theta_{1,k}-\tilde\theta_{i',k}\|,|\tilde\varepsilon_t|\right) < \varepsilon_1:\right. \\
  &\qquad j = 1,\ldots,q_1, k = 1,\ldots,q_2, t = 1,\ldots,T \left.\right\}, \\
  E_2 := &\{\|(\bm{\eta}',\bm{\phi}',\bm{\theta}',\bm{\delta}',\tilde{\bm{\phi}}',\tilde{\bm{\theta}}')'\|_\infty < M_1\},  
\end{align*}
where $\tilde\varepsilon_t = \varepsilon_{1,t} - \varepsilon_{i',t} + D_{i,t}(\varepsilon_{\alpha,1} - \varepsilon_{\alpha,i'})$ and $\bm{\eta},\bm{\phi},\bm{\theta},\bm{\delta},\tilde{\bm{\phi}}$, and $\tilde{\bm{\theta}}$ are vectors containing the random effects in \eqref{random-effects} for indices $1$ and $i'$, and we take $\|\bm{a}\|_\infty = \max_j(|a_j|)$ . We will also suppose that $\|\x_{j,t}\|_\infty < M_1$ for $j \in \{1,i'\}$ and all $t = 1,\ldots,T$. Note that both $\Prob(E_1^C) \to 0$ and $\Prob(E_2^C) \to 0$  as $\sigma^2 \to 0$ with $T$ and $n$ fixed. For simplicity we will set $q_1 = q_2 = 1$.

For all $t > T^*$ let $\tilde y_{i',t}$ possess the same dynamics as $y_{i',t}$ except that this process is shifted in a manner to reflect how $y_{i,t}$ changes for all $t > T^*$. More formally, we will let 
$$
  \tilde y_{i',t} = \left\{\begin{array}{cc}
  y_{i,t} & \text{when} \; t < T^*+1; \\ 
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}y_{1,t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t = T^* + 1; \\
  \eta_1 + \mu_\alpha + \delta_{i'}' \x_{i',T^*+1} + \tilde\phi_{i',t}\tilde y_{i',t} + \tilde\theta_{i'}'\x_{i',t} + \varepsilon_{i',t} + \varepsilon_{\alpha,i'} & \text{when} \; t > T^* + 1.
\end{array}\right.	
$$
The purpose of $\tilde y_{i',t}$ is to place the post-shock responses at the same starting point which allows us to avoid strong parametric specifications on the pre-shock dynamics. This series also contains terms which are estimable from the data. Define the event 
$$
  E_3 := \{\max\left(y_{1,t},\tilde y_{i',t}\right) < M_2 : t = 1,\ldots,T\}, 
$$
where $M_2$ is chosen large enough so that $\Prob(E_3^c) \to 0$ as $\sigma^2 \to 0$. Let $M = \max(M_1,M_2).$ We now consider the recursion of $|y_{1,t} - \tilde{y}_{i',t}|$ for $t > T^*$ conditional on $E = E_1 \cup E_2 \cup E_3$, 
\begin{align*}
	&|y_{1,t} - \tilde{y}_{i',t}| 
		= |(\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1})
		+ (\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}) 
		+ (\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t}) + \tilde\varepsilon_t| \\
	&\qquad \leq |\delta_1'\x_{1,T^*+1} - \delta_{i'}'\x_{i',T^*+1}|
		+ |\tilde\phi_{1}y_{1,t-1} - \tilde\phi_{i'}\tilde{y}_{i',t-1}| 
		+ |\tilde\theta_{1}'\x_{1,t} - \tilde\theta_{i'}'\x_{i',t})| 
		+ \varepsilon_1 \\
	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| + |\tilde\phi_1||y_{1,t-1} - \tilde{y}_{i',t-1}| \\
	&\qquad\leq (8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||y_{i',t-1}| \\ 
	&\qquad\qquad+ |\tilde\phi_1|\left\{(8M + 1)\varepsilon_1 + |\tilde\phi_{1} - \tilde\phi_{i'}||\tilde{y}_{i',t-2}| + |\tilde\phi_1||y_{1,t-2} - \tilde{y}_{i',t-2}|\right\} \\
	&\qquad= \varepsilon_1(8M + 1)(1 + |\tilde\phi_1|) + |\tilde\phi_1||\tilde\phi_{1} - \tilde\phi_{i'}|(|\tilde{y}_{i',t-1}| + |y_{i',t-2}|) + |\tilde\phi_1|^2|y_{1,t-2} - \tilde{y}_{i',t-2}| \\
	&\qquad \leq \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}| + |\tilde\phi_1|^{t-T^*}|y_{1,T^*} - \tilde{y}_{i',T^*}| \\
	&\qquad = \varepsilon_1(8M + 1)\sum_{j=0}^{t-T^*-1}|\tilde\phi_1|^j + |\tilde\phi_{1} - \tilde\phi_{i'}|\sum_{j=1}^{t-T^*}|\tilde\phi_1|^{j-1}|\tilde{y}_{i',t-j}|.
\end{align*}
With $T$ set, we can choose $\varepsilon_1$ small enough so that 
$
  |y_{1,t} - \tilde{y}_{i',t}| < \varepsilon_2
$
for all $T^* < t \leq T $.

@@

We now bound the difference in loss differential vectors $\|\dbf_{1,t} - \dbf_{i',t}\|$ for $t > T^*$ when we specify the loss $L(a,b) = |a-b|$. The loss differential vector $\dbf_{1,t} \in \R^H$ has elements $|y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}|$. What we have showed so far in \eqref{bounds} and \eqref{forecastbounds} allows us to write
$$
  |y_{1,t} - \hat{y}^{1,h}_{1,t}| - |y_{1,t} - \hat{y}^{2,h}_{1,t}| \leq |\tilde{y}_{i',t} - \hat{\tilde{y}}^{i',h}_{1,t}| - |\tilde{y}_{i',t} - \hat{\tilde{y}}^{2,h}_{1,t}| + 2(\varepsilon_3 + \varepsilon_7).
$$
Let $\varepsilon_8 = 2(\varepsilon_3 + \varepsilon_7)$ and conclude that $\|\dbf_{1,t} - \dbf_{i',t}\| \leq \varepsilon_8$ on $E$ for all $t > T^*$.

@@

Recall from Section \ref{forecast}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively). We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence. The weighted voting procedure weight those testing indicators using $\mbf{W}^*$; and returns shock prevalence if the output exceeds 0.5 and shock transience if the output is smaller than 0.5. As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct. From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_0$ and $\mc{M}$ for different $L$. However, weighted voting suggests shock transience for $\mc{M}$ for different $L$ but shock prevalence for $\mc{M}_0$ and $L=15, 30$ and shock transience for $\mc{M}_0$ and $L = 7$. As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small. Note that Proposition \ref{votprop} and Corollary \ref{coro2} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$. Note that the interpretation and meaning of $p_1$ is closely connected with models. For example, $\mc{M}_0$ would imply a persistent shock whereas $\mc{M}$ is more general in suggesting changing dynamics. Thus, even if  this theoretical statement  may be correct, it makes practical sense only when model is identified well. This comment corresponds to the possibility that $\mc{M}_0$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}$.
